MetaTracts - A Method for Robust Extraction and Visualization of Carbon Fiber Bundles in Fiber Reinforced Composites

### 2014-09-01 chapters/MetaTracts.tex
modified abstract + intro

%REPLACED BY 
%Carbon fiber reinforced polymers (CFRP) are promising materials for future components as they allow integrating the continuously rising demands of various industrial  branches.

Carbon fiber reinforced polymers (CFRP) are bundles of individual carbon fibers
woven into sheets of carbon fiber cloth which are layered
and reinforced by an epoxy material.
To manufacture CFRP's, bundles of individual carbon fibers are woven into sheets of carbon fiber cloth which are layered and reinforced by an epoxy matrix. The alignment and weave pattern of the fiber bundles in the cloth influences the strength and stiffness properties of the resulting material. The resulting material shows high specific stiffness, high specific strength, and high corrosion resistance. 
Increasingly, complex primary structures and highly loaded components are being manufactured from CFRP.
Advanced composites and in particular carbon fiber reinforced polymers have thus successfully been introduced in aeronautic and automotive applications. Besides commercial aerospace and automotive industry, CFRP is also being used
in a wide range of applications such as aeronautical, marine and civil engineering, automotive and wind turbine design,
and sporting goods manufacturing.

>>>>

%REPLACED BY 
Modern industry is increasingly demanding function orientation, integration, and efficiency of novel materials and future components. 
The materials of choice of a strongly growing number of industrial branches are carbon fiber reinforced polymers (CFRP), which allow an integration of those continuously rising demands.
Carbon fiber reinforced polymers, more specifically CFRPs with endless carbon fibers which we focus on in this work, typically consist of two main components: 
The matrix, which acts as a glue and the reinforcements, which allows for achieve the desired characteristics. 
Resins such as epoxy are typically used in a CFRP material system with endless carbon fibers for the matrix. 
For special applications additional filler materials, such as colors or other particles, may be integrated. 
However, the most important component is the reinforcement component, which consists in our application case of bundles of endless carbon fibers. 
The carbon fiber bundles are woven into sheets of carbon fiber cloth, which are layered and reinforced by an epoxy material to manufacture a CFRP laminate.
The alignment and weaving pattern of a CFRP laminate strongly influences the strength and stiffness properties of the material. The resulting material shows high specific stiffness, high specific strength, and high corrosion resistance. 
Increasingly, complex primary structures and highly loaded components are being manufactured from CFRP.
Advanced composites and in particular carbon fiber reinforced polymers have thus successfully been introduced in aeronautic and automotive applications. Besides commercial aerospace and automotive industry, CFRP is also being used
in a wide range of applications such as aeronautical, marine and civil engineering, automotive and wind turbine design,
and sporting goods manufacturing.

### 2014-09-01 metaTracts-pvis2014.tex
modified abstract + intro

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{Arindam Bhattacharya\thanks{e-mail: arindamb86@gmail.com}\\ %
        \scriptsize The Ohio State University %
\and Christoph Heinzl\thanks{e-mail:christoph.heinzl@fh-wels.at}\\ %
     \scriptsize University of Applied Sciences Upper Austria. %
\and Rephael Wenger\thanks{e-mail:wenger@cse.ohio-state.edu}\\ %
    \scriptsize The Ohio State University}

@@

%% Abstract section.
\abstract{
Carbon fiber reinforced polymers are bundles of individual carbon fibers woven into sheets of carbon fiber cloth which are layered
and reinforced by an epoxy material. Industrial 3D X-ray computed tomography (XCT) generates a 3D volumetric representation of a scanned object, reconstructed from a series of 2D penetration images,
taken throughout a full rotation of the object.	We describe a technique for extracting and visualizing fiber bundles in fiber reinforced composites scanned with X-ray computed tomography.
Our goal is to visualize the geometric structures of the weaving pattern by analyzing large  areas of  composite woven fabrics using XCT scans of low resolution. Individual fibers are barely visible in such scans. We apply and extend methods originally developed for diffusion tensor imaging (DTI) on the generated XCT data. In the first step a coarse version of integral curves is used to extract sections of the fiber bundles in the woven fabrics. We call these sections MetaTracts.
In the next step the extracted fiber bundle sections are clustered using a two phase approach, wherein we first cluster according to orientation and then  cluster by proximity. We test our algorithm on a number of data sets and show that it effectively identifies and separates different fiber bundles. This work will provide a stepping stone to introduce novel non destructive testing techniques for reinforced fiber bundles analysis.
} % end of abstract

>>>>

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{Arindam Bhattacharya\thanks{e-mail: arindamb86@gmail.com}\\ %
        \scriptsize The Ohio State University %
\and Christoph Heinzl\thanks{e-mail:christoph.heinzl@fh-wels.at}\\ %
     \scriptsize University of Applied Sciences - Upper Austria. %
\and Rephael Wenger\thanks{e-mail:wenger@cse.ohio-state.edu}\\ %
    \scriptsize The Ohio State University}

@@

%% Abstract section.
\abstract{
Carbon fiber reinforced polymers (CFRP) consist of two components: a matrix and a reinforcement. 
The base material for the matrix is typically a resin such as epoxy. 
The reinforcement provides the desired material characteristics. 
In case of CFRPs the reinforcements are typically bundles of individual carbon fibers (henceforth referred to as fiber bundle) woven into sheets of carbon fiber cloth which are layered and reinforced by an epoxy material. 
For quality control of CFRP materials and components industrial 3D X-ray computed tomography (XCT) is increasingly applied as it allows detailed characterizations of the material in a non-destructive manner.

This work contributes to the state of the art of CFRP characterization by the introduction of MetaTracts, a technique for extracting and visualizing fiber bundles and the geometric structure of the weaving pattern in fiber reinforced composites scanned with X-ray computed tomography. 
The declared goal of this work is to analyzing large areas of CFRPs using XCT scans of low resolution, in which individual fibers are barely visible. 
To reach this goal we apply and extend methods originally developed for diffusion tensor imaging (DTI) on the generated XCT data. 
In the first step a coarse version of integral curves is used to extract sections of the fiber bundles in the woven fabrics. We call these sections MetaTracts.
Next, the extracted fiber bundle sections are clustered using a two step approach, wherein we first cluster according to orientation and then  cluster by proximity. 
We evaluate our algorithm on a number of data sets and demonstrate that MetaTracts effectively and robustly identifies and separates different fiber bundles. 
%mention user study here?%
This work will provide a stepping stone to introduce novel non destructive testing techniques for reinforced fiber bundles analysis.
} % end of abstract
